---
title: "Assignment Submission"
author: "fllbck"
date: "Friday, March 13, 2015"
output: html_document
---

Initialization

```{r}
rm(list=ls())
set.seed(3)
require(caret)
source('~/Dropbox/Jeff\'s course/assignment/pml_write_files.R')
```

Read in Training data

```{r}
df<-read.table("pml-training.csv", header=T, sep=',')
```

Select the numeric columns
```{r}
num<- sapply(df, is.numeric)
df2=df[,num]
```
Then I realized many of these numeric columns mostly have NA's in them, so I decided to remove these columns too.

```{r}
df3 = df2[, colSums(is.na(df2)) == 0]
```
Then I attached the output colume to df3
```{r}
df3$classe = df$classe
```
I guess the timestamp doesn't really help, so I throw them away
```{r}
df3 = df3[, -c(2,3)]
```

Start training a neural network model

````{r}
md <- train(classe~.,
            data = df3,
            method = 'rf',
            number = 3,
            repeats = 3,
            ntree = 100)
```

Read in test data and select the columns used in training data
```{r}
testData = read.table('pml-testing.csv', header = T, sep=',')
testData2 = testData[, which(names(testData) %in% names(df3))]
```
Predict results
```{r}
class_predict_prob = predict(md, newdata = testData2, type = 'prob')
View(class_predict_prob)
```
Export final results by using the code provided 
```{r}
predict = predict(md, newdata = testData2)
pml_write_files(predict)
```


